### 2022-07-27 manuscript.tex
Merge pull request #266 from SORTEE-Github-Hackathon/RCO-iss263 [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/50a63631e17fef9d3b6a8798a25b2567c940fca3.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/50a63631e17fef9d3b6a8798a25b2567c940fca3/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/2745745268

This manuscript
(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/0aaaf3e6a685b4c96e2115ee2f709dab93a233f8/}{permalink})
was automatically generated
from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/0aaaf3e6a685b4c96e2115ee2f709dab93a233f8}{SORTEE-Github-Hackathon/manuscript@0aaaf3e}
on July 26, 2022.

@@

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 0\tabcolsep) * \real{1.0000}}@{}}
\toprule
\begin{minipage}[b]{\linewidth}\raggedright
Ten tips for getting started in GitHub
\end{minipage} \\
\midrule
\endhead
1. \textbf{Check for an existing solution to your problem.} The GitHub Help webpage (\url{https://docs.github.com/en}) contains extensive and detailed documents with helpful screenshots. It is a good starting point for handling an issue, and has troubleshooting tips for specific problems. Alternatively, consider Tweeting your issue. There is a large community of GitHub users around the world who have likely faced analogous problems and may be able to provide quick solutions. Third, try to follow blogs (\emph{e.g.}, \url{https://github.blog}), Twitter accounts or YouTube channels that regularly post practical solutions about the most widely-used web platform for common GitHub issues. \\
2. \textbf{Consider taking free courses}, such as those from Software Carpentry\textsuperscript{\protect\hyperlink{ref-pjy75gHr}{73}}, and sharing these courses with your lab members or colleagues. \\
3. \textbf{Take advantage of GitHub as an asynchronous working tool for team-based projects.} See the repository for this paper (\url{https://github.com/SORTEE-Github-Hackathon/manuscript}) as an example of a collaboratively authored manuscript that used the GitHub Discussions, Issues, Pages, and Actions features. \\
4. \textbf{The GitHub Learning Lab (\url{https://lab.github.com})} allows you to learn GitHub basics through short projects and tasks, and allows you to get feedback from their Learning Lab bot. \\
5. \textbf{Learn markdown and use cheatsheets (\emph{e.g.}, \url{http://markdownguide.org/basic-syntax})} so you can write clear metadata README files for your repositories. \\
6. \textbf{Consult the Jenny Bryan Universe of GitHub material,} which provides a thorough and accessible introduction for a multitude of research-related uses for GitHub, and includes a book\textsuperscript{\protect\hyperlink{ref-ZvrOcg9w}{74}}, statistics course\textsuperscript{\protect\hyperlink{ref-6CMMeSeD}{75}} and academic article\textsuperscript{\protect\hyperlink{ref-RVetqmsg}{7}}. \\
7. \textbf{Do not be afraid of trial-and-error.} One of the best ways to learn GitHub is the ``trial-and-error'' method. Learning from your own mistakes can be a valuable way to master your GitHub abilities. In any case, if you make mistakes, GitHub allows you to revert any steps that you desire via version controlling. \\
8. \textbf{If you are an educator, include lectures on reproducibility and tools for creating reproducible workflows in the curricula.} Some graduate programs include coursework on course R Markdown and GitHub. Getting students started with these tools earlier will prevent the resistance that comes from working with a less reproducible workflow for a longer period of time. (see example \url{https://github.com/rmcelreath/stat_rethinking_2022}) \\
9. \textbf{Try to begin committing with graphical user interfaces (GUI) instead of command line interfaces (CLI).} Examples of GUI are the GitHub Desktop (\url{https://desktop.github.com}), git-gui (\url{https://git-scm.com/docs/git-gui}), RStudio (\url{https://www.rstudio.com}), Visual Studio Code (\url{https://code.visualstudio.com}), Atom (\url{https://atom.io}), GitKraken (\url{https://www.gitkraken.com}). \\
10. \textbf{Get help deciphering GitHub Notifications.} Try using tools like Octobox (\url{https://octobox.io}) to disentangle and manage multiple notifications from distinct GitHub projects. \\
\bottomrule
\end{longtable}

>>>>

This manuscript
(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/50a63631e17fef9d3b6a8798a25b2567c940fca3/}{permalink})
was automatically generated
from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/50a63631e17fef9d3b6a8798a25b2567c940fca3}{SORTEE-Github-Hackathon/manuscript@50a6363}
on July 27, 2022.

@@

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 0\tabcolsep) * \real{1.0000}}@{}}
\toprule
\begin{minipage}[b]{\linewidth}\raggedright
Ten tips for getting started in GitHub
\end{minipage} \\
\midrule
\endhead
1. \textbf{Check for an existing solution to your problem.} The GitHub Help webpage (\url{https://docs.github.com/en}) contains extensive and detailed documents with helpful screenshots. It is a good starting point for handling an issue, and has troubleshooting tips for specific problems. Alternatively, consider Tweeting your issue. There is a large community of GitHub users around the world who have likely faced analogous problems and may be able to provide quick solutions. Third, try to follow blogs (\emph{e.g.}, \url{https://github.blog}), Twitter accounts or YouTube channels that regularly post practical solutions about the most widely-used web platform for common GitHub issues. \\
2. \textbf{Consider taking free courses}, such as those from Software Carpentry\textsuperscript{\protect\hyperlink{ref-pjy75gHr}{73}}, and sharing these courses with your lab members or colleagues. \\
3. \textbf{Take advantage of GitHub as an asynchronous working tool for team-based projects.} See the repository for this paper (\url{https://github.com/SORTEE-Github-Hackathon/manuscript}) as an example of a collaboratively authored manuscript that used the GitHub Discussions, Issues, Pages, and Actions features. \\
4. \textbf{The GitHub Skills page (\url{https://skills.github.com/})} allows you to learn GitHub basics through short projects and tasks with step-by-step guides. \\
5. \textbf{Learn markdown and use cheatsheets (\emph{e.g.}, \url{http://markdownguide.org/basic-syntax})} so you can write clear metadata README files for your repositories. \\
6. \textbf{Consult the Jenny Bryan Universe of GitHub material,} which provides a thorough and accessible introduction for a multitude of research-related uses for GitHub, and includes a book\textsuperscript{\protect\hyperlink{ref-ZvrOcg9w}{74}}, statistics course\textsuperscript{\protect\hyperlink{ref-6CMMeSeD}{75}} and academic article\textsuperscript{\protect\hyperlink{ref-RVetqmsg}{7}}. \\
7. \textbf{Do not be afraid of trial-and-error.} One of the best ways to learn GitHub is the ``trial-and-error'' method. Learning from your own mistakes can be a valuable way to master your GitHub abilities. In any case, if you make mistakes, GitHub allows you to revert any steps that you desire via version controlling. \\
8. \textbf{If you are an educator, include lectures on reproducibility and tools for creating reproducible workflows in the curricula.} Some graduate programs include coursework on course R Markdown and GitHub. Getting students started with these tools earlier will prevent the resistance that comes from working with a less reproducible workflow for a longer period of time. (see example \url{https://github.com/rmcelreath/stat_rethinking_2022}) \\
9. \textbf{Try to begin committing with graphical user interfaces (GUI) instead of command line interfaces (CLI).} Examples of GUI are the GitHub Desktop (\url{https://desktop.github.com}), git-gui (\url{https://git-scm.com/docs/git-gui}), RStudio (\url{https://www.rstudio.com}), Visual Studio Code (\url{https://code.visualstudio.com}), Atom (\url{https://atom.io}), GitKraken (\url{https://www.gitkraken.com}). \\
10. \textbf{Get help deciphering GitHub Notifications.} Try using tools like Octobox (\url{https://octobox.io}) to disentangle and manage multiple notifications from distinct GitHub projects. \\
\bottomrule
\end{longtable}
